Structured Versus Decorated Cospans

### 2020-11-19 cospans.tex
added reference for proof of Thm. 2.3 (in Kenny's thesis).

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/11/18

@@

\begin{thm}
Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\lCsp \to F'\lCsp$ as defined above.
Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\mathsf{A'}$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F'$} (D);
\end{tikzpicture}
\]
\end{thm}

Details of the constructions and the proof of the above theorem can be found at \cite{CourserThesis}.

>>>>

% Structured versus decorated cospans
% John Baez, Kenny Courser and Christina Vasilakopoulou
% in LaTeX
% 2020/11/19

@@

\begin{thm}
Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal (strong) double functor $\mathbb{H} \maps F\lCsp \to F'\lCsp$ as defined above.
Given two finitely cocomplete categories $\A$ and $\A'$, two symmetric lax monoidal pseudofunctors $F \maps \A \to \Cat$ and $F' \maps \A' \to \Cat$, a finite colimit preserving functor $H \maps \A \to \A'$, a symmetric lax monoidal pseudofunctor $E \maps \Cat \to \Cat$ and a 2-isomorphism $\theta \maps EF \Rightarrow F' H$ as in the following diagram, the triple $(H,E,\theta)$ induces a symmetric monoidal double functor $\lH \maps F\lCsp \to F'\lCsp$ as defined above.
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$\A$};
\node (B) at (1,0) {$\Cat$};
\node (C) at (0,-1) {$\mathsf{A'}$};
\node (C) at (0,-1) {$\A'$};
\node (D) at (1,-1) {$\Cat$};
\node (E) at (0.5,-0.5) {$\Swarrow \theta$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$F$} (B)
(A) edge node[left]{$H$} (C)
(B) edge node[right]{$E$} (D)
(C) edge node[above]{$F'$} (D);
\end{tikzpicture}
\]
\end{thm}

\begin{proof}  See \cite[Theorem 4.2.1]{CourserThesis}. \end{proof}
